Directionality in Kilo-ton Scale Scintillating Neutrino Detectors

### 2013-07-16 Direction.tex
Add acknowledgements. --Lindley

\section{Acknowledgements}
Matt, Henry, Janet, Katsushi. Need Andrey's DOE numbers.

>>>>

\section{Acknowledgements}
The authors would like to thank H. Frisch for useful discussion and comments in preparing this work. The authors would like to thank K. Arisaka for discussion on the capabilities of traditional PMTs in addition to HPDs. Finally, L. Winslow would like to thank J.M. Conrad for suggesting that the LAPPD may have sufficient timing resolution to allow the reconstruction of the electron direction in $0\nu\beta\beta$ and that a collaboration with the University of Chicago should be pursued.  A. Elagin and M. Wetstein are supported by DOE XXXX. C. Aberle and L. Winslow are supported by funds from University of California Los Angeles.
